### 2014-11-11 conclusions.tex
Rewrite some text.

We have presented a novel way of adding coordination to a declarative language without
changing the nature of the language or introducing non-declarative constructs. We
took advantage of the fact that CLM uses linear logic, which allows us to derive
coordination facts that can be deleted in order to perform actions in the underlying
runtime system. In the other hand, sensing facts allow the programmer to reason
about locality and scheduling of computation in a data-driven fashion.
We have presented several applications where a judicious use of coordination can lead to
better performance behavior.

We would like to explore this coordination paradigm in distributed systems,
where data locality is far more important than in shared memory systems. We also
think that CLM may be useful as a glue distributed/parallel language since it can
easily model any computation pattern using graphs. Furthermore, we think that
other declarative paradigms would benefit from using a similar approach. For
instance, in functional programming, one may consider annotation functions that
pick the right granularity for each problem.

>>>>

We have presented a novel way of adding coordination to a declarative language without
changing the nature of the language or introducing non-declarative constructs. We
took advantage of the fact that CLM uses linear logic, which allows us to derive
coordination facts that can be deleted in order to perform actions in the underlying
runtime system. In the other hand, sensing facts allow the programmer to reason
about locality and scheduling of computation in a data-driven fashion.
Even though the programs are optimized, the proofs of correctness for CLM
programs remain simple since coordination does not change the language.

We would like to explore CLM's coordination principles in distributed systems,
where data locality is far more important than in shared memory systems.
Furthermore, we think that other declarative paradigms would benefit
from giving programmers the freedom to fine-tune their programs while keeping
the program declarative and easy to reason about.

### 2014-11-11 intro.tex
Update Related Work.
Rewrite some text.

In this paper, we introduce Coordinated Linear Meld (CLM), a declarative
language that extends the Linear Meld~(LM) language~\cite{cruz-iclp14,cruz-ppdp14} with coordination facts that give programmer
control over scheduling and data placement. LM is a linear logic programming
language designed for programs that operate on graphs.  The use of linear
logic~\cite{girard-87} supports structured manipulation of mutable
state. In LM, computation is divided so that each node of the graph computes
independently and is allowed to \scare{communicate} with other nodes.
Both computation and communication happen through the derivation of logical
rules (which make up the program).

>>>>

In this paper, we introduce Coordinated Linear Meld (CLM), a data-centric declarative
language that extends the Linear Meld~(LM)
language~\cite{cruz-iclp14,cruz-ppdp14} with coordination facts that give
programmer control over scheduling and data placement. LM is a linear logic
programming language designed for programs that operate on graphs.  The use
of linear logic~\cite{girard-87} supports structured manipulation of mutable
state. In LM, computation is divided so that each node of the graph computes
independently and is allowed to \scare{communicate} with other nodes.  Both
computation and communication happen through the derivation of logical rules
(which make up the program).
